---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# adbc

<!-- badges: start -->
[![rcc](https://github.com/r-dbi/adbc/workflows/rcc/badge.svg)](https://github.com/r-dbi/adbc/actions)
[![Codecov test coverage](https://codecov.io/gh/r-dbi/adbc/branch/master/graph/badge.svg)](https://codecov.io/gh/r-dbi/adbc?branch=master)
<!-- badges: end -->

adbc is an DBI-compliant interface to databases supporting the experimental adbc database.

## Installation

Install from GitHub via

```r
# install.packages("devtools")
devtools::install_github("r-dbi/adbc")
```

## Example

Requires duckadbc from <https://github.com/r-dbi/duckadbc>:

- Clone the repository
- Install the R package with `R CMD INSTALL tools/rpkg`

```{r}
library(adbc)
library(DBI)

drv <- adbc(asNamespace("duckadbc")$.__NAMESPACE__.$DLLs$duckadbc[["path"]], "duckdb_adbc_init")

con <- dbConnect(drv)

dbExecute(con, "CREATE TABLE a (x INTEGER, y FLOAT)")

dbExecute(con, "INSERT INTO a (x, y) VALUES (0, 0.5), (1, 1.5), (2, 2.5)")

dbGetQuery(con, "SELECT * FROM a WHERE x > 1")

dbGetQueryArrow(con, "SELECT * FROM a WHERE x > 1")

as.data.frame(dbGetQueryArrow(con, "SELECT * FROM a WHERE x > 1"))

dbDisconnect(con)
```

## Update vendored files

Via `tools/adbc.sh`, currently requires a clean checkout at a specific path.

---

Please note that the 'adbc' project is released with a
[Contributor Code of Conduct](CODE_OF_CONDUCT.md).
By contributing to this project, you agree to abide by its terms.
